FTLR proof cases

### 2018-05-22 fully-abstract-comp/ftlr-proof-cases.tex
Added the remaining cases for FTLR proof refactoring.

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
  \begin{itemize}
  \item $\trust = \trusted \vee \npair{(\baddr,\eaddr)} \in \readCond{\lin,W}$
  \item $\npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}$
  \end{itemize}
  and one of the following sets of requirements holds:
  \begin{enumerate}[label={\roman*)}]
  \item \begin{itemize}
    \item $W \vdash_{(\ta,\stkb)} (\mscode,\_,\_,\_,\sigrets,\sigcloss)$
    \item $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \trusted$
    \item For all $\npair{\stpair{\reg}{\reg}} \in \lrrtrusted(W)$ and $\memSat{\src{\ms_S},\src{\ms_\stk},\src{\stk},\ms_T}{W}$ and $\ms_f$, we have $\src{\Phi} = (\src{\ms_S} \uplus \ms_f, \src{reg_S}, \src{\stk}, \src{\ms_\stk})$ and 
      \begin{itemize}           
      \item $\src{\Phi}$ checks $\stkb$ before calls in $\ta$ for $n$ steps (Definition~\ref{def:check-stack-addr-before-call}).
      \item $\src{\Phi}$ uses link seals properly in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:use-return-seals-call}).
      \item $\src{\Phi}$ handle trusted seals properly in $\ta$ with components parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:handle-trusted-seals-properly}).
      \item $\src{\Phi}$ does not store link seals and code capabilities in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:never-store-seal-code-cap}).
      \end{itemize}
    \end{itemize}
  \item
    \begin{itemize}
    \item $[\baddr,\eaddr] \mathrel{\#} \ta$
    \item $\trust = \untrusted$
    \end{itemize}
  \end{enumerate}
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lreg{\trust}(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

@@

\item All of the following hold: (includes simple cases: gettype, geta, getb, gete, getp, getl, lt, plus, minus, that can be handled uniformly)

@@

\item All of the following hold: (includes memory-manipulation cases: jmp, jnz, xjmp, that can be handled mostly uniformly)
  \begin{itemize}
  \item 
  \end{itemize}
\end{itemize}

>>>>

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
  \begin{itemize}
  \item $\trust = \trusted \vee \npair{(\baddr,\eaddr)} \in \readCond{\lin,W}$
  \item $\npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}$
  \end{itemize}
  and one of the following sets of requirements holds:
  \begin{enumerate}[label={\roman*)}]
  \item \begin{itemize}
    \item $W \vdash_{(\ta,\stkb)} (\mscode,\_,\_,\_,\sigrets,\sigcloss)$
    \item $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \trusted$
    \item For all $\npair{\stpair{\reg}{\reg}} \in \lrrtrusted(W)$ and $\memSat{\src{\ms_S},\src{\ms_\stk},\src{\stk},\ms_T}{W}$ and $\ms_f$, we have $\src{\Phi} = (\src{\ms_S} \uplus \ms_f, \src{reg_S}, \src{\stk}, \src{\ms_\stk})$ and 
      \begin{itemize}           
      \item $\src{\Phi}$ checks $\stkb$ before calls in $\ta$ for $n$ steps (Definition~\ref{def:check-stack-addr-before-call}).
      \item $\src{\Phi}$ uses link seals properly in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:use-return-seals-call}).
      \item $\src{\Phi}$ handle trusted seals properly in $\ta$ with components parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:handle-trusted-seals-properly}).
      \item $\src{\Phi}$ does not store link seals and code capabilities in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:never-store-seal-code-cap}).
      \end{itemize}
    \end{itemize}
  \item
    \begin{itemize}
    \item $[\baddr,\eaddr] \mathrel{\#} \ta$
    \item $\trust = \untrusted$
    \end{itemize}
  \end{enumerate}
and show
\[
\npair{(c,c)} \in \lreg{\trust}(W)
\]
For $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

@@

\item All of the following hold: (includes simple cases: gettype, geta, getb,
  gete, getp, getl, lt, plus, minus, one case of move that can be handled uniformly)

@@

\item All of the following hold: (includes control-flow manipulation cases: jmp, jnz, xjmp, that can be handled mostly uniformly)
  \begin{itemize}
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item One of the following holds
    \begin{itemize}
    \item(jnz) $\Phi_S' = \updPcAddr{\Phi_S}$ and $\Phi_T' = \updPcAddr{\Phi_T}$
    \item(jmp,jnz) $\Phi_S' = \Phi_S\updReg{\pcreg,r_1}{\Phi_S(r_1),w_1}$ and $\Phi_T' =
      \Phi_T\updReg{\pcreg,r_1'}{\Phi_T(r_1),w_1'}$ and 
      $\isLinear{\Phi_S(r_1)} \Rightarrow w_1 = w_1' = 0$ and
      $\neg \isLinear{\Phi_S(r_1)} \Rightarrow (w_1 = \Phi_S(r_1) \text{ and }
      w_1' = \Phi_T(r_1))$
    \item(xjmp) $\Phi_S(r_1) = \sealed{\sigma,c_1}$ and $\Phi_S(r_2) =
      \sealed{\sigma,c_2}$ and $\Phi_T(r_1) = \sealed{\sigma,c_1'}$ and
      $\Phi_T(r_2) = \sealed{\sigma,c_2'}$ and $\Phi_S'(r_1,r_2) =
      \linCons{c_1},\linCons{c_2}$ and $\Phi_T'(r_1,r_2) =
      \linCons{c_1'},\linCons{c_2'}$ and\\
      $c_1' \neq \retptrc(\_)$ and $c_2' \neq \retptrd(\_)$ and
        $\nonExec{c_\data}$ and $\Phi_T'(\pcreg,\rdata) = c_1',c_2'$ and
      one of the following hold:
      \begin{itemize}
      \item $c_1 \neq \retptrc(\_)$ and $c_2 \neq \retptrd(\_)$ and
        $\nonExec{c_\data}$ and $\Phi_S'(\pcreg,\rdata) = c_1,c_2$.
      \item $c_1 = \retptrc(\baddr,\eaddr,\aaddr)$, and $c_2 =
        \retptrd(\aaddr_\stk,\eaddr_{\stk,\priv})$ and $\Phi(r_\stk) =
        \stkptr{\rw,\stkb,\eaddr_\stk,\_}$ and $\Phi_S.\stk = \stk_\var{frame}
        :: (\aaddr,\ms_{\stk,\priv})$ and
        $\dom(\ms_{\stk,\priv} = [\eaddr_\stk+1,\eaddr_{\stk,\priv}])$ and
        $\Phi_S'.\ms_\stk = \ms_{\stk,\priv} \uplus \Phi_S.\ms_\stk$ and
        $\Phi_S'.\stk = \stk$ and
        \[
          \begin{split}
\Phi_S' = \Phi_S&[\pcreg \mapsto ((\rx,\normal),\baddr,\eaddr,\aaddr)]\\
            &[\rstk \mapsto
            \stkptr{\rw,\stkb,\eaddr_{\stk,\priv},e_\stk+1}] \\
            &[\rdata,\rtmp{1},\rtmp{2},r_2 \mapsto 0, 0, 0, 0]
          \end{split}
        \]
      \end{itemize}
    \end{itemize}
  \end{itemize}
\end{itemize}
